Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-08 conclusion.tex
refine conclusion.

We characterized the experience by evaluating the efficiency, scalability and
reliability of both PanDA Broker and AthenaMP as deployed on Titan
(\S\ref{sec:panda_titan}). Our characterization highlighted the strengths and
limitations of the current design and implementation: PanDA Brokers enable
the sustained execution of millions of simulations per week but further work
is required to optimize its efficiency and reliability
(\S\ref{ssec:broker_titan}). PanDA Brokers support the concurrent execution
of multiple AthenaMP instances, enabling each AthenaMP to perform the
concurrent execution of up to 16 Geant4 simulators. Nonetheless, our
characterization showed how improving I/O performance could reduce overheads
(\S\ref{ssec:athenamp_titan}), increasing the overall utilization of Titan's
backfill availability.

@@

The development of NGE is looking forward to deal with these challenges by providing an abstraction layer for HPC resources together with a set of APIs for the coordination and fast deployment of heterogeneous workloads.

>>>>

We characterized the experience by evaluating the efficiency, scalability and
reliability of both PanDA Broker and AthenaMP as deployed on Titan
(\S\ref{sec:panda_titan}). Our characterization highlighted the strengths and
limitations of the current design and implementation: PanDA Brokers enable the
sustained execution of millions of simulations per week but further work is
required to optimize its efficiency and reliability
(\S\ref{ssec:broker_titan}). PanDA Brokers support the concurrent execution of
multiple AthenaMP instances, enabling each AthenaMP to perform the concurrent
execution of up to 16 Geant4 simulators. Nonetheless, our characterization
showed how improving I/O performance could reduce overheads
(\S\ref{ssec:athenamp_titan}), increasing the overall utilization of Titan's
backfill availability. We introduced PanDA's next generation executor for HPC
systems, characterized its ability to support multi-generation workloads and
analyzed its scaling behavior. It enables the high-performance execution of
new workloads and advanced execution modes of traditional workloads.

@@
